Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
vobj syntax
vobj: details

\begin{frame}{${\nu}Obj$: Syntax}
\begin{itemize}
\item terms in ${\nu}Obj$ denote objects or classes; consist of:
\begin{itemize}
\item variables $x$ denoting objects
\item selections $t.l$
\item object creations
\item \mbox{$\newin{x \larrowc t}{u}$} defining an object $x$ of class $t$
whose scope is the term $u$
\item class templates $\cls{x: S \sep \tup d}$,
\item mixin compositions $t \withsub{S} u$ denoting a class of self
type $S$ combined from two classes $t$ and $u$
\end{itemize}
\item a value is a variable or class template
\item a path is a variable followed by a possibly empty sequence of selections
\item types in ${\nu}Obj$ consist of:
\begin{itemize}
\item singleton types $p.\type$
\item type selections $T\Tsel L$
\item record types $\obj{x \sep \tup D}$
\item compound types $T \with U$
\item class types $\cls{x: S \sep \tup D}$.
\end{itemize}
\end{itemize}
\end{frame}

>>>>

\begin{frame}{${\nu}Obj$: Syntax}
\begin{itemize}
\item terms in ${\nu}Obj$ denote objects or classes; consist of:
\begin{description}[mixin compositions]
\item[variables] $x$
\item[selections] $t.l$
\item[object creations] \mbox{$\newin{x \larrowc t}{u}$}
\item[class templates] $\cls{x: S \sep \tup d}$
\item[mixin compositions] $t \withsub{S} u$
\end{description}
\item a value is a variable or class template
\item a path is a variable followed by a possibly empty sequence of selections
\item types in ${\nu}Obj$ consist of:
\begin{description}[mixin compositions]
\item[singleton types] $p.\type$
\item[type selections] $T\Tsel L$
\item[record types] $\obj{x \sep \tup D}$
\item[compound types] $T \with U$
\item[class types] $\cls{x: S \sep \tup D}$
\end{description}
\end{itemize}
\end{frame}

\begin{frame}{${\nu}Obj$: Details}
\begin{itemize}
\item type bindings
\begin{description}[abstract types]
\item[type aliases] $=$
\item[new types] $\expand$
\item[abstract types] $<:$
\end{description}
\item class template $\cls{x: S \sep \tup d}$ related to translucent sum; some differences:
\begin{itemize}
\item needs to be instantiated
\item ``contractive'' restriction
\end{itemize}
\item class type $\cls{x: S \sep \tup D}$
\begin{itemize}
\item contains as values classes that instantiate to objects of (sub)type $\obj{x \sep \tup D}$
\item explicit self type $S$ may be different from $\obj{x \sep \tup D}$
\item declarations in $S$ which are not in $\tup D$ play the role of abstract members, defined by mixin composition during instantiation
\end{itemize}
\end{itemize}
\end{frame}
